\sysfull

### 2018-08-07 paper/asplos19/systemdescription.tex
revisions of system description

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/system-overview.pdf}
	\caption{\sys top-level view. ATS: adaptive task scheduler, PP: Page Privatizer, PM: physical memory.}
	\label{fig:system_overview}
\end{figure}

\sys is a new programming and execution model for intermittent operation on energy-harvesting devices. It addresses the challenges given in Section~\ref{sec:background} making task-based intermittent applications {\em programmable}, {\em efficient} and {\em portable}, introducing a new programming model and runtime software system that supports adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/system-overview.pdf}
	\caption{\sys top-level view. APP: application, ATS: adaptive task scheduler, VMM: Virtual Memory Manager, PM: physical memory.}
	\label{fig:system_overview}
\end{figure}

\sys is a new programming and execution model for intermittent operation on \emph{small embedded energy-harvesting devices}. It addresses the challenges given in Section~\ref{sec:background} making task-based intermittent applications {\em programmable}, {\em efficient} and {\em portable}, introducing a new programming model and runtime software system that supports adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.
